---
title: "Midterm Presentation"
author: "Group 10: Kayla Choi, Kosuke Sasaki, Clare Zike Tan, Franky Yifan Zhang"
date: "11/3/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Introduction and Research Question
- Data comes from USDA National Agricultural Statistics Service
- over 10000 observations of 13 variables

Questions:  
Does the type of chemical have a correlation to the amount of strawberries produced (Measured in lb / acre / application )?   
  
Do different states use different chemicals?   
  
How do the amount of strawberries produced differ by state?   


## Data Manipulation
```{r, include = FALSE}
source("data_and_eda.R")
```
- Combined strawberry and pesticide csv
- Created a function to drop rows with NA data or columns with only 1 value.   
- Separated messy variable names into tidy, useable variables  


## EDA: Plot 1

```{r, fig.cap = "Relative Frequency of Chemical use per year", echo = FALSE, fig.dim = c(8,3)}
chem_year_valueq
```
  
For both fungicide and insecticide, the use generally goes down every year, which we can see from the increasing 1st quartile (pink) and decreasing 4th quartile (purple).    
Let's visualize the difference between fungicide and insecticide.    
  

## EDA: Plot 2
```{r, fig.cap = "Distribution of Chemical use and corresponding strawberry production", echo = FALSE, fig.dim = c(8,4)}
violin
```
  
Insecticide has higher mean and median value, but fungicide has a larger spread.   
Let's look at this information in a different way. 

## EDA: Plot 3
```{r, fig.cap = "Density of Chemical use and corresponding strawberry production", echo = FALSE, fig.dim = c(8,3)}
density
```
  
Same conclusions as before:  
- Fungicide corresponds with lower strawberry production  
- Insecticide has higher values  
- Fungicide has larger spread  


## Combining Year and State questions
Let's consider the trend of strawberry production corresponding to different chemicals by state and by year.   
We can do this with interactive plot.  

## Interactive Plot 1: Fungicide
```{r, fig.cap = "Strawberry production per acre per fungicide application over time by state", echo = FALSE, fig.dim = c(8,4)}
ggplotly(p_f)
```
  
This decreases over time, which makes sense if you recall the first slide of relative frequency.    
  
## Interactive Plot 2: Insecticide
```{r, fig.cap = "Strawberry production per acre per insecticide application over time by state", echo = FALSE, fig.dim = c(8,4)}
ggplotly(p_i)
```
  
This plot is more irregular. 
    
## Map and shiny

Let's turn to the Shiny app for a closer look at chemical by state and for a map.  
Then, let's come back for conclusions.  

## Conclusion
- Strawberry produced by acre by application has decreased over time.  
-  

## Extra EDA
In our data exploration, we created many other plots:    
- Bee toxicity vs strawberry production  
- Bee toxic chemicals used in CA versus other states  
- Bee toxic chemicals used in CA by toxicity level  
- Interactive plot of chemical and strawberry production by both year and state    
Let us know if you would like to see these extra plots.    
